Running simulations of MultipleContactNeutralMigrat.nlogo

### 2023-10-10 RunSims.Rmd
Many changes

}

@@

# Neutral communities 
#
mdl <- sloss_sim %>% filter(deforestation_type == "regular",birds_behavior=="NoSelection")
names(mdl)
#
# Plot for neutral communities
# Calculate the power exponent 
# pexp = (1 - 2 * birds_dispersal_distance ) / (1 - birds_dispersal_distance ), median_dispersal_distance = 2^(1/pexp-1) 
#
mdl1 <- mdl %>% mutate(habitat_patch_size = habitat_patch_size+1) %>%
                         group_by(birds_dispersal_distance, habitat_patch_size,birth_rate_birds) %>% summarise(across(c(birds_at_deforestation:count_birds,max_patch),list(mean=mean, sd=sd, ql=~quantile(.x,probs=c((1-0.95)/2)), qh=~quantile(.x,probs=c(1-(1-0.95)/2)) )))

@@

@@

mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.8)
    )

@@

# Shannon-Diversity  
#
mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Shannon Diversity") +
  theme(
    legend.position = c(0.9,0.8)
    )

@@

#
# Number of species by max_patch size 
# 
mdl1  %>% #filter(birds_dispersal_distance %in% c(1.1,1.5,3)) %>%
  ggplot(aes(x = max_patch_mean, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)) ,  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Max patch size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.8)
    )

@@

# Neutral communities 
#
mdl <- sloss_sim %>% filter(deforestation_type == "random block", birds_behavior == "NoSelection")
names(mdl)
#
# Plot for neutral communities 
#
mdl1 <- mdl %>% mutate(habitat_patch_size = habitat_patch_size+1) %>%
                         group_by(birds_dispersal_distance, habitat_patch_size,birth_rate_birds) %>% summarise(across(c(birds_at_deforestation:count_birds,max_patch) ,list(mean=mean, sd=sd, ql=~quantile(.x,probs=c((1-0.95)/2)), qh=~quantile(.x,probs=c(1-(1-0.95)/2)) ))) #  %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/

@@

#
# Number of species by patch block size
#
mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.8)
    )

@@

#
# Number of species by max_patch size 
# 
mdl1  %>% #filter(birds_dispersal_distance %in% c(1.1,1.5,3)) %>%
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)) ,  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Max patch size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.83)
    )

@@

#
# shannon_diversity by max_patch size 
# 
mdl1  %>% # filter(birds_dispersal_distance %in% c(1.1,1.5,3)) %>%
  ggplot(aes(x = max_patch_mean, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)) ,  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Max patch size") + ylab("Shannon Diversity") +
  theme(
    legend.position = c(0.9,0.2)
    )

@@

mdl <- sloss_sim %>% filter(deforestation_type == "regular", birds_behavior=="Hierarchical")
names(mdl)
#
# summarize data 
#
mdl1 <- mdl %>% mutate(habitat_patch_size = habitat_patch_size+1) %>%
                         group_by(birds_dispersal_distance, habitat_patch_size,birth_rate_birds) %>% summarise(across(birds_at_deforestation:count_birds,list(mean=mean, sd=sd, ql=~quantile(.x,probs=c((1-0.95)/2)), qh=~quantile(.x,probs=c(1-(1-0.95)/2)) ))) #  %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/ birds_at_deforestation  )
names(mdl1)

@@

mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.3,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.8)
    )

@@

# Shannon-Diversity  
#
mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.3,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.8)
    )

@@

## Not fragmented communities Lambda = 1.7 - 4

```{r SLOSS_notfrag_simulations, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
require(tidyverse)

source("R/functions.r")

# Not fragmented communities = habitat_patch_size = 100
#
mdl <- read_netlogo_simul("Simulations/NoHiBi_pf00_hpf3_dd1-3_lambda1.7-4.csv") %>% mutate(habitat_patch_size=100)

# New Simulations 
#
mdl <- read_netlogo_simul("Simulations/NoHiBi_pf00_hpf3_dd1-3_lambda1.1-4.csv") %>% mutate(habitat_patch_size=100)

# Add Migration0_at_deforestation=FALSE to previous simulations 
#
unique(sloss_sim$Migration0_at_deforestation)
sloss_sim <- sloss_sim %>% mutate( Migration0_at_deforestation = if_else(is.na(Migration0_at_deforestation), FALSE, Migration0_at_deforestation )) 
unique(sloss_sim$habitat_patch_size)
#sloss_sim <- sloss_sim %>% mutate( habitat_patch_size = if_else(habitat_patch_size==0, 100, habitat_patch_size ))

saveRDS(sloss_sim, "Simulations/sloss_sim.rds")

names(mdl)
#
# Plot for neutral communities 
# I filter birth_rate_birds 1.1 because these communities survive only by migration
#
mdl1 <- mdl %>% filter(birth_rate_birds!=1.1) %>% group_by(birds_dispersal_distance, birth_rate_birds,birds_behavior) %>% summarise(across(birds_at_deforestation:count_birds,mean)) %>% mutate(birth_rate_birds = factor(birth_rate_birds)  )

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_number_of_species,color=birth_rate_birds)) + geom_point() + geom_line() + scale_color_viridis_d(name="lambda") + facet_wrap( ~birds_behavior )  + theme_bw() + ylab("Number of species") + xlab("Dispersal Distance") 
ggsave("Figures/Species_NoFrag_Dispersal_Lambda.png",width=8,height=6,units="in",dpi=600)

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_shannon_diversity,color=birth_rate_birds)) + geom_point() + scale_color_viridis_d() + facet_wrap( ~birds_behavior ) + theme_bw()

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=count_birds,color=birth_rate_birds)) + geom_point() + geom_line() + scale_color_viridis_d(name="lambda") + facet_wrap( ~birds_behavior )  + theme_bw() + ylab("Number of indiv.") + xlab("Dispersal Distance") 
ggsave("Figures/Indiv_NoFrag_Dispersal_Lambda.png",width=8,height=6,units="in",dpi=600)

mdl1 %>% filter(birds_dispersal_distance == 1.1 || birds_dispersal_distance == 3) %>%  mutate(birds_dispersal_distance=factor(birds_dispersal_distance)) %>% ggplot(aes(x=birth_rate_birds,y=calc_number_of_species,color=birds_dispersal_distance)) + geom_point() + scale_color_viridis_d() + theme_bw()+ facet_wrap( ~birds_behavior )

@@

## Add more simulations lambda = 2 with Migration

```{r SLOSS_combined_plots, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}

mdl <- read_netlogo_simul("Simulations/NoHiBi_pf06_hpf3-61_dd1-3_lambda2_Migrat.csv")

mdl <- read_netlogo_simul("Simulations/NoHiBi_pf06_hpf3-61_dd1-3_lambda2_NoMigrat.csv") 
sloss_sim <- bind_rows(sloss_sim,mdl)

mdl <- read_netlogo_simul("Simulations/NoHiBi_pf06_hpf3-61_dd1-3_lambda4_Migrat.csv") 
sloss_sim <- bind_rows(sloss_sim,mdl)

save.image()

#
# 200 x 200 - Started simulation 10:47
#
mdl <- read_netlogo_simul("Simulations/NoHiBi_200_pf06_hpf3-61_dd1-3_lambda2_NoMigrat.csv")
sloss_sim <- bind_rows(sloss_sim,mdl)
sloss_sim <- sloss_sim %>% mutate( world_width=if_else(is.na(world_width),100,world_width))
sloss_sim <- sloss_sim %>% mutate( world_width=if_else(world_width==99,100,world_width))

saveRDS(sloss_sim, "Simulations/sloss_sim.rds")

@@

## Plots of combined behaviors and patch 100

```{r SLOSS_combined_plots1, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
require(tidyverse)

source("R/functions.r")

#mdl1 <- sloss_sim %>% filter(Migration0_at_deforestation | (birth_rate_birds==2 & habitat_patch_size==100)) %>%  
sloss_sim %>% distinct(Migration0_at_deforestation, world_width)

#
# Count number of simulations
#
mdl1 <- sloss_sim %>% filter(Migration0_at_deforestation, world_width==100 ) %>%  
  count(habitat_patch_size,birds_dispersal_distance, birth_rate_birds,birds_behavior)

mdl1 <- sloss_sim %>% filter(Migration0_at_deforestation, world_width==100 ) %>%  
  group_by(habitat_patch_size,birds_dispersal_distance, birth_rate_birds,birds_behavior) %>%
  summarise(across(birds_at_deforestation:count_birds,mean)) %>% mutate(birth_rate_birds = factor(birth_rate_birds)  )

#mdl1 %>% filter(birds_dispersal_distance == 1.1 || birds_dispersal_distance == 3 || birds_dispersal_distance == 1.5) %>%  
mdl1 %>% mutate(birds_dispersal_distance=factor(birds_dispersal_distance)) %>% ggplot(aes(x=habitat_patch_size,y=calc_number_of_species,color=birds_dispersal_distance)) + geom_point() + geom_line() + scale_color_viridis_d(name="Dispersal") + theme_bw()+ facet_wrap( ~birds_behavior ) + ylab("Number of species") + xlab("Patch Size") + ggtitle("Lambda=2 Degraded 60% NoMigration")

ggsave("Figures/Species_PatchSize_Dispersal_NoMigration.png",width=8,height=6,units="in",dpi=600)

>>>>

} else if(Sys.info()['nodename'] =="MacLeonardo.local") {                     # Mac
  simfolder <- "~/Dropbox/Projects/DynamicForestExtinction"
}

@@

# Neutral communities 
#
mdl <- sloss_sim %>% filter(deforestation_type == "regular",birds_behavior=="NoSelection", habitat_patch_size != 199)
names(mdl)
#
# Plot for neutral communities
# Calculate the power exponent 
# pexp = (1 - 2 * birds_dispersal_distance ) / (1 - birds_dispersal_distance ), median_dispersal_distance = 2^(1/pexp-1) 
#
mdl1 <- mdl %>% mutate(habitat_patch_size = habitat_patch_size+1) %>%
                         group_by(birds_dispersal_distance, habitat_patch_size,birth_rate_birds) %>% summarise(across(c(birds_at_deforestation:count_birds,max_patch,degraded_mfp,non_degraded_mfp),list(mean=mean, sd=sd, ql=~quantile(.x,probs=c((1-0.95)/2)), qh=~quantile(.x,probs=c(1-(1-0.95)/2)) )))

@@

mdl1 %>%  
  ggplot(aes(x = max_patch_mean, y = degraded_mfp_mean, color = factor(habitat_patch_size))) + 
  geom_point(  size = 1.2) + guides(color = "none") #+

mdl1 %>%  
  ggplot(aes(x = max_patch_mean, y = non_degraded_mfp_mean, color = factor(habitat_patch_size))) + 
  geom_point(  size = 1.2) + guides(color = "none") #+

mdl1 %>%  
  ggplot(aes(x = degraded_mfp_mean, y = non_degraded_mfp_mean, color = factor(habitat_patch_size))) + 
  geom_point(  size = 1.2) + guides(color = "none") #+

@@

mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.8)
    )

@@

# Shannon-Diversity  
#
mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Shannon Diversity") +
  theme(
    legend.position = c(0.9,0.8)
    )

@@

#
# Number of species by max_patch size 
# 
mdl1  %>% #filter(birds_dispersal_distance %in% c(1.1,1.5,3)) %>%
  ggplot(aes(x = max_patch_mean, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Max patch size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.8)
    )

@@

# Neutral communities 
#
mdl <- sloss_sim %>% filter(deforestation_type == "random block", birds_behavior == "NoSelection")
names(mdl)
#
# Plot for neutral communities 
#
mdl1 <- mdl %>% mutate(habitat_patch_size = habitat_patch_size+1) %>%
                         group_by(birds_dispersal_distance, habitat_patch_size,birth_rate_birds) %>% summarise(across(c(birds_at_deforestation:count_birds,non_degraded_mfp,degraded_mfp,max_patch) ,list(mean=mean, sd=sd, ql=~quantile(.x,probs=c((1-0.95)/2)), qh=~quantile(.x,probs=c(1-(1-0.95)/2)) ))) #  %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/

@@

mdl1 %>%  
  ggplot(aes(x = max_patch_mean, y = degraded_mfp_mean, color = factor(habitat_patch_size))) + 
  geom_point(  size = 1.2) + guides(color = "none") #+

mdl1 %>%  
  ggplot(aes(x = max_patch_mean, y = non_degraded_mfp_mean, color = factor(habitat_patch_size))) + 
  geom_point(  size = 1.2) + guides(color = "none") #+

mdl1 %>%  
  ggplot(aes(x = degraded_mfp_mean, y = non_degraded_mfp_mean, color = factor(habitat_patch_size))) + 
  geom_point(  size = 1.2) + guides(color = "none") #+

#
# Number of species by patch block size
#
mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.8)
    )

@@

#
# Number of species by max_patch size 
# 
mdl1  %>% #filter(birds_dispersal_distance %in% c(1.1,1.5,3)) %>%
  ggplot(aes(x = max_patch_mean, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Max patch size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.83)
    )

@@

#
# shannon_diversity by max_patch size 
# 
mdl1  %>% # filter(birds_dispersal_distance %in% c(1.1,1.5,3)) %>%
  ggplot(aes(x = max_patch_mean, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Max patch size") + ylab("Shannon Diversity") +
  theme(
    legend.position = c(0.9,0.2)
    )

@@

mdl <- sloss_sim %>% filter(deforestation_type == "regular", birds_behavior=="Hierarchical", habitat_patch_size != 199)
names(mdl)
#
# summarize data 
#
mdl1 <- mdl %>% mutate(habitat_patch_size = habitat_patch_size+1) %>%
                         group_by(birds_dispersal_distance, habitat_patch_size,birth_rate_birds) %>% summarise(across(birds_at_deforestation:count_birds,list(mean=mean, sd=sd, ql=~quantile(.x,probs=c((1-0.95)/2)), qh=~quantile(.x,probs=c(1-(1-0.95)/2)) ))) #  %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/ birds_at_deforestation  )
names(mdl1)

@@

mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.3,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.8)
    )

@@

# Shannon-Diversity  
#
mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.3,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.8)
    )

@@

# Plot for birth selection communities regular patterns

```{r ExploratoryPlotsSelectionRegular, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}

mdl <- sloss_sim %>% filter(deforestation_type == "regular", birds_behavior=="BirthSelection", habitat_patch_size != 199)
names(mdl)
#
# summarize data 
#
mdl1 <- mdl %>% mutate(habitat_patch_size = habitat_patch_size+1) %>%
                         group_by(birds_dispersal_distance, habitat_patch_size,birth_rate_birds) %>% summarise(across(birds_at_deforestation:count_birds,list(mean=mean, sd=sd, ql=~quantile(.x,probs=c((1-0.95)/2)), qh=~quantile(.x,probs=c(1-(1-0.95)/2)) ))) #  %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/ birds_at_deforestation  )
names(mdl1)

mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.3,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.8)
    )

ggsave("Figures/Selection_Species_Dispersal_Lambda_regular.png",width=8,height=6,units="in",dpi=600)

# Shannon-Diversity  
#
mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.3,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Shannon Diversity") +
  theme(
    legend.position = c(0.9,0.8)
    )

ggsave("Figures/Selection_Shannon_Dispersal_Lambda_regular.png",width=8,height=6,units="in",dpi=600)

@@

## Plots across neutral hierarchical selection modelos regular fragmentation

```{r PlotsAcrossBehaviorRegular, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}

mdl <- sloss_sim %>% filter(deforestation_type == "regular", habitat_patch_size != 199)
names(mdl)
#
# summarize data 
#
mdl1 <- mdl %>% mutate(habitat_patch_size = habitat_patch_size+1) %>%
                         group_by(birds_dispersal_distance, habitat_patch_size,birth_rate_birds,birds_behavior) %>% summarise(across(birds_at_deforestation:count_birds,list(mean=mean, sd=sd, ql=~quantile(.x,probs=c((1-0.95)/2)), qh=~quantile(.x,probs=c(1-(1-0.95)/2)) ))) #  %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/ birds_at_deforestation  )
names(mdl1)

mdl1 %>%  filter(birth_rate_birds == 2) %>% 
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birds_behavior), fill = factor(birds_dispersal_distance)), alpha = 0.3,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birds_behavior, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.8)
    )

ggsave("Figures/AcrossBehav_Species_Dispersal_Lambda2_regular.png",width=8,height=6,units="in",dpi=600)

# Shannon-Diversity  
#
mdl1 %>%  filter(birth_rate_birds == 2) %>% 
  ggplot(aes(x = habitat_patch_size, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birds_behavior), fill = factor(birds_dispersal_distance)), alpha = 0.3,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birds_behavior, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Shannon Diversity") +
  theme(
    legend.position = c(0.9,0.8)
    )

ggsave("Figures/AcrossBehav_Shannon_Dispersal_Lambda2_regular.png",width=8,height=6,units="in",dpi=600)

@@

## Plots across neutral hierarchical selection modelos regular fragmentation

```{r PlotsAcrossBehaviorRegular, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}

mdl <- sloss_sim %>% filter(birds_behavior=="NoSelection", habitat_patch_size != 199)
names(mdl)
#
# summarize data 
#
mdl1 <- mdl %>% mutate(habitat_patch_size = habitat_patch_size+1) %>%
                         group_by(birds_dispersal_distance, habitat_patch_size,birth_rate_birds,deforestation_type) %>% summarise(across(c(birds_at_deforestation:count_birds,mean_patch,degraded_mfp,non_degraded_mfp),list(mean=mean, sd=sd, ql=~quantile(.x,probs=c((1-0.95)/2)), qh=~quantile(.x,probs=c(1-(1-0.95)/2)) ))) #  %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/ birds_at_deforestation  )
names(mdl1)

mdl1 <- mdl1 %>%  mutate(across(mean_patch_mean:mean_patch_qh,sqrt))

mdl1 %>%  filter(birth_rate_birds == 2) %>% 
  ggplot(aes(x = mean_patch_mean, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, deforestation_type), fill = factor(birds_dispersal_distance)), alpha = 0.3,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ deforestation_type, ncol = 2) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.8)
    )
